---
title: "p8105_hw1_xz3312"
author: "Eric Zhang"
date: "2025-09-17"
output: html_document
---
#Problem 1
##Loading package and dataset
```{r}
install.packages("moderndive")
library(moderndive)
data("early_january_weather")
skimr::skim(early_january_weather)
```

##Dataset description
The dataset early january weather shows hourly weather observations of Newark in January 2013. The dataset describes Newark weather conditions using variables
```{r}
paste(names(early_january_weather)[6:15],collapse = ",")
```
which includes temperature, dew point, humidity, wind direction, wind speed, wind gust, precipitation, pressure, and visibility. Additionally, the dataset size is
```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```
which is 358 rows and 15 columns. The mean temperature of the dataset is 39.58212 degrees Fahrenheit, as shown here
```{r}
mean(early_january_weather$temp)
```


##Make a scatter plot of temp vs time(hour)
```{r}
library(ggplot2)

ggplot(early_january_weather, aes(x=time_hour,y=temp,color=humid))+
  geom_point()+
  scale_color_viridis_c()+
  labs(title = "EWR January Temperature vs Time",
        x = "Time (hour)", y = "Temperature (F)", color = "Humidity(%)")+
  theme_minimal()
```

#Problem 2





