---
title: "p8105_hw1_xz3312"
author: "Eric Zhang"
date: "2025-09-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(moderndive)
library(ggplot2)
library(dplyr)
data("early_january_weather", package = "moderndive")
```

##Dataset description
The dataset early january weather shows hourly weather observations of Newark in January 2013. The dataset describes Newark weather conditions using variables
```{r}
paste(names(early_january_weather)[6:15],collapse = ",")
```
which includes temperature, dew point, humidity, wind direction, wind speed, wind gust, precipitation, pressure, and visibility. Additionally, the dataset size is
```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```
which is 358 rows and 15 columns. The mean temperature of the dataset is 39.58212 degrees Fahrenheit, as shown here
```{r}
mean(early_january_weather$temp)
```


##Make a scatter plot of temp vs time(hour) from ewr january weather dataset
```{r}
library(ggplot2)




ewr_plot <- ggplot(early_january_weather,
                   aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  scale_color_viridis_c() +
  labs(title = "EWR January Temperature vs Time",
       x = "Time (hour)", y = "Temperature (F)",
       color = "Humidity (%)") +
  theme_minimal()


ewr_plot

ggsave("ewr_plot.png", plot = ewr_plot, width = 7, height = 5, dpi = 300)

```

#Problem 2
##Create a dataframe
```{r}
library(tidyverse)
set.seed(1234)
x <- rnorm(10)
plot_df = tibble(
  sample_size = x,
  is_positive = x>0,
  character_vec = sample(letters,10),
  factor_vec = factor(sample(
    c("A","B","C"), 10, replace = TRUE
  ))
)

str(plot_df)
```
##Take the mean of each variable in dataframe
```{r}
mean(plot_df$sample_size)
mean(plot_df$is_positive)
mean(plot_df$character_vec)
mean(plot_df$factor_vec)
```
Taking the mean of the whole dataframe results in error, argument is not numeric or logical. Therefore, the mean of each column needs to be taken separately. It's also worth noting the mean of character vector and factor vector are NA, because they are text strings not numeric values so taking the mean is not possible.

##Apply as.numeric to convert to numeric
```{r}
as.numeric(plot_df$is_positive)
as.numeric(plot_df$character_vec)
as.numeric(plot_df$factor_vec)
```
Logical vector can be converted to numeric values and its mean can be taken and logically interpreted, with True = 1 and False = 0. Character vector consists of texts that cannot be converted to numeric values hence the as.numeric function result is NA. Factor vector can be converted to numeric values that represent the letter: A = 1, B = 2, C = 3. However, it is meaningless to take the mean of factor vector because it's used for classification.







